Fusion Moves for Correlation Clustering

### 2014-10-27 paper/egpaper_for_review.tex
future work

\begin{itemize}
  \item Multicut in computer vision, applications, sparse segmentation -> IMPORTANT PROBLEM
  \item Problem: Existing Methods does not scale, even CGC. - Large scale 3d problems
  \item Contribution: Fast scalable method using novel fusion moves for correlation clustering
\end{itemize}

@@

>>>>

%$\rho_y : E \to E_y$
%$\rho_y^{-1} : E_y \to E$

$\rho_y : P(G) \to P(G_y)$

$\rho_y^{-1} : P(G_y) \to P(G)$
\begin{itemize}
  \item Multicut in computer vision, applications, sparse segmentation -> IMPORTANT PROBLEM
  \item Problem: Existing Methods does not scale, even CGC. - Large scale 3d problems
  \item Contribution: Fast scalable method using novel fusion moves for correlation clustering
\end{itemize}

@@

\section{Further Work}
So far we have generated the proposals randomly and do not take the current segmentation into account.

So far we only enforce must link constraints to obtain smaller problems.
One can also enforce must-not link constraints to the problem. 
If those are closed, they automatically lead to a decomposition of the problem, which is a interesting property for very huge data.
